Preprocing and mergind datasets

### 2021-08-19 intero_study_preprocessing.Rmd
Update intero_study_preprocessing.Rmd

@@

now cleaning
we need to have data for ledalab
gaze path
clean and tracloss

@@

# now read them
setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Step1_GpExtractor_Output")

@@

  # tmp.df2$right_pupil_measure1<- if_else(tmp.df2$pupil_meas>7, tmp.df2$right_pupil_measure1, NULL)
  message(sprintf("step 4 cutingt off screen in points and repixel"))
  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$left_gaze_x_cor >= -960 & tmp.df2$left_gaze_x_cor <= 960, tmp.df2$left_gaze_x_cor, NULL)
  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$right_gaze_x_cor >= -960 & tmp.df2$right_gaze_x_cor <= 960, tmp.df2$right_gaze_x_cor, NULL)

@@

# let's check to see if it looks fine
ggplot(tmp.df3, aes(time, gsr, colour = as.factor(ssid)))+
  geom_line()
  # facet_grid(~screencontent)

@@

# fill up
   tmp.df3<- tmp.df3%>%
      arrange(time)%>%
     group_by(ssid, tNo)%>%
      fill(zero_stim, .direction = c('up'))
   tmp.df3$timerezero2<- tmp.df3$time-tmp.df3$zero_stim
   # check timerezero2

@@

#tmp.df3<- subset(tmp.df3, is.na(tmp.df3$ssid) == FALSE)

ggplot(subset(tmp.df3, tmp.df3$Condition == 'IAPS') , aes(x = timerezero3, y= gsr, colour = as.factor(ssid)))+
    geom_smooth()+
    # geom_()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

ggplot(subset(tmp.df3, tmp.df3$tNo == -4) , aes(x = timerezero2, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

```{r}
tmp.df3<- tmp.df3%>%
  arrange(ssid, time,tNo)
# gsr baseline wil be the 1 second before tial start
# gsr to microsiemnes 1/J3*100000

@@

tmp.df3<- tmp.df3 %>%
  group_by(ssid, trialUnq) %>%
  mutate(extendpupil=extend_blinks(pupil, fillback=100, fillforward=100, hz=150))

@@

tmp.df3 <- smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
                                    extendblinks=TRUE, step.first= 'smooth',
                                    maxgap=Inf, 
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

@@

ggplot(subset(tmp.df3, tmp.df3$tNo == 10 & tmp.df3$ssid == 320) , aes(x = timerezero3, y= pup_interp, colour = as.factor(ssid)))+
  geom_line()+
  geom_line(aes(y = pupil), colour = 'gray')
  # facet_grid(~Condition)

>>>>

# for some reason 355 is creating duplicate event ids
library(readr)
ss355_GPdata_ <- read_csv("ss355_GPdata .csv")

View(ss355_GPdata_)

ss355_GPdata_nodup <- subset(ss355_GPdata_, !duplicated(ss355_GPdata_$event_id))

write_csv(ss355_GPdata_nodup, "ss355_GPdata_nodup.csv")

@@

now cleaning
we need to have data for ledalab
gaze path
clean and trackloss

@@

# now read them
# setwd("D:/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Step1_GpExtractor_Output")
setwd("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/Eyetracking/2021/step1")

@@

  # tmp.df2$right_pupil_measure1<- if_else(tmp.df2$pupil_meas>7, tmp.df2$right_pupil_measure1, NULL)
  message(sprintf("step 4 cuting off screen in points and repixel"))
  tmp.df2$left_gaze_x_cor<- if_else(tmp.df2$left_gaze_x_cor >= -960 & tmp.df2$left_gaze_x_cor <= 960, tmp.df2$left_gaze_x_cor, NULL)
  tmp.df2$right_gaze_x_cor<- if_else(tmp.df2$right_gaze_x_cor >= -960 & tmp.df2$right_gaze_x_cor <= 960, tmp.df2$right_gaze_x_cor, NULL)

@@

# let's check to see if it looks fine - NOTE THIS IS a bit SLOW
ggplot(tmp.df3, aes(time, gsr, colour = as.factor(ssid)))+
  geom_line()
  # facet_grid(~screencontent)

@@

# fill up
   tmp.df3<- tmp.df3%>%
      arrange(time)%>%
     group_by(ssid, tNo)%>%
      fill(zero_stim, .direction = c('up'))

tmp.df3$timerezero2<- tmp.df3$time-tmp.df3$zero_stim
   # check timerezero2

@@

#tmp.df3<- subset(tmp.df3, is.na(tmp.df3$ssid) == FALSE)
tmp.df3%>%
subset(Condition == 'IAPS' & ssid ==  353)%>%
  ggplot(aes(x = timerezero3, y= gsr))+
  stat_smooth()+
    # geom_smooth()+
    # geom_()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

tmp.df3%>%
subset( tNo == -5)%>%
  ggplot( aes(x = timerezero2, y= gsr, colour = as.factor(ssid)))+
  # geom_point()
      geom_line() +
    # geom_smooth(aes())+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

```{r}

tmp.df3<- tmp.df3%>%
  arrange(ssid, time,tNo)
# gsr baseline wil be the 1 second before tial start
# gsr to microsiemnes 1/J3*100000

@@

tmp.df3<- tmp.df3 %>%
  group_by(ssid, trialUnq,tNo,screencontent) %>%
  mutate(extendpupil=extend_blinks(pupil, fillback=100, fillforward=100, hz=150))

@@

?smooth_interpolate_pupil

tmp.df3 <- smooth_interpolate_pupil(tmp.df3, pupil="pupil", extendpupil="extendpupil",
                                    extendblinks=TRUE, step.first= 'smooth/interpolate',
                                    maxgap=Inf, 
                                    filter = 'moving',
                                    type="linear", hz=150, n = 5)

tmp.df3<-tmp.df3 %>%
  group_by(ssid, trialUnq,tNo,screencontent) %>%
  smooth_interpolate_pupil(pupil="pupil", extendpupil="extendpupil",
                                    extendblinks=TRUE, 
                           step.first= 'smooth',
                                    maxgap=10, 
                                    filter = 'moving',
                                    type="linear", hz=20, n = 10)

tmp.df3<- tmp.df3 %>%
  group_by(ssid, trialUnq,tNo,screencontent) %>%
  smooth_interpolate_pupil(pupil="extendpupil", extendpupil="extendpupil",
                                    extendblinks=TRUE, step.first= 'smooth/interpolate',
                                    maxgap=100, 
                                    filter = 'moving',
                                    type="linear", hz=150, n = 30)

@@

subset(tmp.df3, tNo == 20 & ssid == 347)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   geom_line(aes(y = extendpupil), color = 'red')+
  geom_line(aes(y = pupil), colour = 'gray')
  # facet_grid(~Condition)

subset(tmp.df3, tNo == -7 & ssid == 350)%>%
ggplot(aes(x = timerezero3, y= pupil))+
  geom_line()

subset(tmp.df3, tNo == -7 & ssid == 350)%>%
ggplot(aes(x = timerezero3, y= pup_interp))+
  geom_line()+
   geom_line(aes(y = extendpupil), color = 'red')
  geom_line(aes(y = pup_interp), colour = 'gray')
  # facet_grid(~Condition)
```
